TY  - JOUR
AU  - Brunton, Lucy A.
AU  - Alexander, Neil
AU  - Wint, William
AU  - Ashton, Adam
AU  - Broughan, Jennifer M.
PY  - 2017
DA  - 2017/02/01
TI  - Using geographically weighted regression to explore the spatially heterogeneous spread of bovine tuberculosis in England and Wales
JO  - Stochastic Environmental Research and Risk Assessment
SP  - 339
EP  - 352
VL  - 31
IS  - 2
AB  - An understanding of the factors that affect the spread of endemic bovine tuberculosis (bTB) is critical for the development of measures to stop and reverse this spread. Analyses of spatial data need to account for the inherent spatial heterogeneity within the data, or else spatial autocorrelation can lead to an overestimate of the significance of variables. This study used three methods of analysis—least-squares linear regression with a spatial autocorrelation term, geographically weighted regression (GWR) and boosted regression tree (BRT) analysis—to identify the factors that influence the spread of endemic bTB at a local level in England and Wales. The linear regression and GWR methods demonstrated the importance of accounting for spatial differences in risk factors for bTB, and showed some consistency in the identification of certain factors related to flooding, disease history and the presence of multiple genotypes of bTB. This is the first attempt to explore the factors associated with the spread of endemic bTB in England and Wales using GWR. This technique improves on least-squares linear regression approaches by identifying regional differences in the factors associated with bTB spread. However, interpretation of these complex regional differences is difficult and the approach does not lend itself to predictive models which are likely to be of more value to policy makers. Methods such as BRT may be more suited to such a task. Here we have demonstrated that GWR and BRT can produce comparable outputs.
SN  - 1436-3259
UR  - https://doi.org/10.1007/s00477-016-1320-9
DO  - 10.1007/s00477-016-1320-9
ID  - Brunton2017
ER  - 
