PMID- 32602300
OWN - NLM
STAT- MEDLINE
DCOM- 20200730
LR  - 20201218
IS  - 1840-2445 (Electronic)
IS  - 1840-0132 (Linking)
VI  - 17
IP  - 2
DP  - 2020 Aug 1
TI  - Spatio-temporal data visualization for monitoring of control measures in the 
      prevention of the spread of COVID-19 in Bosnia and Herzegovina.
PG  - 265-274
LID - 10.17392/1215-20 [doi]
AB  - Aim The damage caused by the COVID-19 pandemic has made the prevention of its 
      further spread at the top of the list of priorities of many governments and state 
      institutions responsible for health and civil protection around the world. This 
      prevention implies an effective system of epidemiological surveillance and the 
      application of timely and effective control measures. This research focuses on the 
      application of techniques for modelling and geovisualization of epidemic data with 
      the aim of simple and fast communication of analytical results via geoportal. 
      Methods The paper describes the approach applied through the project of establishing 
      the epidemiological location-intelligence system for monitoring the effectiveness of 
      control measures in preventing the spread of COVID-19 in Bosnia and Herzegovina. 
      Results Epidemic data were processed and the results related to spatio-temporal 
      analysis of the infection spread were presented by compartmental epidemic model, 
      reproduction number R, epi-curve diagrams as well as choropleth maps for different 
      levels of administrative units. Geovisualization of epidemic data enabled the 
      release of numerous information from described models and indicators, providing 
      easier visual communication of the spread of the disease and better recognition of 
      its trend. Conclusion The approach involves the simultaneous application of epidemic 
      models and epidemic data geovisualization, which allows a simple and rapid 
      evaluation of the epidemic situation and the effects of control measures. This 
      contributes to more informative decision-making related to control measures by 
      suggesting their selective application at the local level.
CI  - Copyright© by the Medical Assotiation of Zenica-Doboj Canton.
FAU - Ponjavić, Mirza
AU  - Ponjavić M
AD  - International Burch University, Sarajevo, Bosnia and Herzegovina.
FAU - Karabegović, Almir
AU  - Karabegović A
AD  - Electrical Engineering Faculty, University of Sarajevo, Sarajevo, Bosnia and 
      Herzegovina.
FAU - Ferhatbegović, Elvir
AU  - Ferhatbegović E
AD  - GAUSS Centre for Geospatial Research Sarajevo, Bosnia and Herzegovina.
FAU - Tahirović, Emin
AU  - Tahirović E
AD  - International University of Sarajevo, Sarajevo, Bosnia and Herzegovina.
FAU - Uzunović, Selma
AU  - Uzunović S
AD  - Department of Clinical Microbiology, Institute for Health and Food Safety Zenica, 
      Zenica, Bosnia and Herzegovina.
FAU - Travar, Maja
AU  - Travar M
AD  - University Clinical Centre of the Republic of Srpska, Banja Luka, Bosnia and 
      Herzegovina.
FAU - Pilav, Aida
AU  - Pilav A
AD  - Institute for Public Health of Sarajevo Canton, Sarajevo, Bosnia and Herzegovina.
FAU - Mulić, Maida
AU  - Mulić M
AD  - Institute for Public Health of Tuzla Canton, Tuzla, Bosnia and Herzegovina.
FAU - Karakaš, Sead
AU  - Karakaš S
AD  - Institute for Public Health of Central Bosnia Canton, Travnik, Bosnia and 
      Herzegovina.
FAU - Avdić, Nermin
AU  - Avdić N
AD  - Institute for Public Health of Herzegovina-Neretva Canton, Mostar, Bosnia and 
      Herzegovina.
FAU - Mulabdić, Zarina
AU  - Mulabdić Z
AD  - Institute for Public Health of Una-Sana Canton, Bihać, Bosnia and Herzegovina.
FAU - Pavić, Goran
AU  - Pavić G
AD  - Institute for Public Health of Posavina Canton, Orašje, Bosnia and Herzegovina.
FAU - Bičo, Medina
AU  - Bičo M
AD  - Institute for Public Health of Bosnian-Podrinje Canton, Goražde, Bosnia and 
      Herzegovina.
FAU - Vasilj, Ivan
AU  - Vasilj I
AD  - Institute for Public Health of West Herzegovina Canton, Grude, Bosnia and 
      Herzegovina.
FAU - Mamić, Diana
AU  - Mamić D
AD  - Institute for Public Health of Herzeg-Bosnian Canton, Livno, Bosnia and Herzegovina.
FAU - Hukić, Mirsada
AU  - Hukić M
AD  - Academy of Sciences and Arts of Bosnia and Herzegovina, Sarajevo, Bosnia and 
      Herzegovina.
LA  - eng
PT  - Journal Article
PL  - Bosnia and Herzegovina
TA  - Med Glas (Zenica)
JT  - Medicinski glasnik : official publication of the Medical Association of Zenica-Doboj 
      Canton, Bosnia and Herzegovina
JID - 101250177
SB  - IM
MH  - Betacoronavirus
MH  - Bosnia and Herzegovina/epidemiology
MH  - COVID-19
MH  - *Communicable Disease Control
MH  - Coronavirus Infections/epidemiology/*prevention & control/transmission
MH  - Data Visualization
MH  - Epidemics
MH  - Epidemiological Monitoring
MH  - Geographic Mapping
MH  - Health Information Systems
MH  - Humans
MH  - Models, Statistical
MH  - Pandemics/*prevention & control
MH  - Pneumonia, Viral/epidemiology/*prevention & control/transmission
MH  - SARS-CoV-2
MH  - *Spatio-Temporal Analysis
OTO - NOTNLM
OT  - COVID 19 pandemic
OT  - decision making
OT  - epidemiological techniques
OT  - geocoding
OT  - health information systems
OT  - reproduction number
EDAT- 2020/07/01 06:00
MHDA- 2020/07/31 06:00
CRDT- 2020/07/01 06:00
PHST- 2020/06/11 00:00 [received]
PHST- 2020/06/14 00:00 [revised]
PHST- 2020/06/20 00:00 [accepted]
PHST- 2020/07/01 06:00 [pubmed]
PHST- 2020/07/31 06:00 [medline]
PHST- 2020/07/01 06:00 [entrez]
AID - 10.17392/1215-20 [doi]
PST - ppublish
SO  - Med Glas (Zenica). 2020 Aug 1;17(2):265-274. doi: 10.17392/1215-20.
